Using pressure-driven flow systems to evaluate laser speckle contrast imaging

### 2022-06-29 article.tex
Update microfluidic syringe pump vs. pressure citations

Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output. A survey of over 20 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments. The devices were from a variety of manufacturers and featured various syringe sizes and materials. Syringe pumps operate by applying mechanical force on the plunger of a syringe at a controlled speed. A rotating lead screw driven by a stepper motor controls the velocity of the plunger, which is calculated based on the syringe size and inner diameter to achieve a desired flow rate. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Korczyk:2010eu,Li:2014ca}. Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump system.

Pressure-driven flow control systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Korczyk:2010eu,Li:2014ca,Zhou:2011ey}. These systems use pressure-regulated air to push liquid from a reservoir through the microfluidic device at a constant flow rate. In order to control the applied pressure, an absolute flow sensor must be added inline with the microfluidic device. Thermal mass flow sensors are commonly used to measure the low flow rates found in microfluidics. These sensors use heating and temperature-sensing elements to detect the magnitude and direction of flow and are factory-calibrated to measure absolute flow rates for various fluids. Integration of the flow sensor with a feedback loop allows for the programming of specific flow rates rather than pressure levels.

>>>>

Syringe pumps are the most widely used flow control system in microfluidic studies and are believed to provide a highly-controlled flow output. A survey of over 20 LSCI studies using microfluidics that were published since 2015 found that syringe pumps were used in the majority (90\%) of experiments. The devices were from a variety of manufacturers and featured various syringe sizes and materials. Syringe pumps operate by applying mechanical force on the plunger of a syringe at a controlled speed. A rotating lead screw driven by a stepper motor controls the velocity of the plunger, which is calculated based on the syringe size and inner diameter to achieve a desired flow rate. However, syringe pumps produce oscillations in flow with varying frequency and magnitude due to the physical motion of the motor and from imperfections on the lead screw \cite{Li:2014ca,Zeng.2014}. Syringe pumps have also been shown to have slow responsivity and can take a long time to achieve programmed flow rates \cite{Zhou:2011ey}. The trade-off between stability and responsivity makes it difficult \cite{Kang.2012} to obtain both stable flow and a fast flow response with a syringe pump system.

Pressure-driven flow control systems overcome the limitations of syringe pumps by eliminating the use of a motor and lead screw to provide very stable flow \cite{Zhou:2011ey,Li:2014ca,Zeng.2020}. These systems use pressure-regulated air to push liquid from a reservoir through the microfluidic device at a constant flow rate \cite{Zeng.2020}. In order to control the applied pressure, an absolute flow sensor must be added inline with the microfluidic device. Thermal mass flow sensors are commonly used to measure the low flow rates found in microfluidics. These sensors use heating and temperature-sensing elements to detect the magnitude and direction of flow and are factory-calibrated to measure absolute flow rates for various fluids. Integration of the flow sensor with a feedback loop allows for the programming of specific flow rates rather than pressure levels.
